Manifold Destiny - or how to rig an election

### 2024-07-07 index.qmd
abc
csv

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
---

# Manifold Destiny - or how to rig an election
**Based upon the ideas developed by Edward K. Solomon**
![](pngs/md.png)

@@

This is a webR-enabled code cell in a Quarto HTML document.

```{webr-r}
fit = lm(mpg ~ am, data = mtcars)
summary(fit)
```

Abc

>>>>

---
title: "Manifold Destiny - or how to rig an election"
output: github_document
execute: 
  cache: false
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table','readr']             # Pre-install dependencies
  cell-options:
    autorun: true
filters:
  - panelize
  - webr
---

```{r, echo=F}
# script/R/simulations.R
```

**Based upon the ideas developed by Edward K. Solomon**
![](pngs/md.png)

# Testing
## Installling packages
```{webr-r}
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
```

## Loading  data
```{webr-r}
dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
```

```{webr-r}
ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
ad
```

@@

```{r, echo=F}
knitr::knit_exit()
```

{{< audio file="abc.mp3" caption="Sample Audio File">}}

```{webr-r}
webr::mount(
  mountpoint = "/data",
  source = "https://example.com/output.data"
)
```
